Using Monte Carlo to estimate the effects of NHL rule changes

### 2020-12-10 slides.Rmd
re add conclusion slide

>>>>

# Conclusion

- The rule changes put in place in 2013 did make it less "fair" for the East teams which have a harder time making the playoffs in comparison to the West teams.
- Adding an additional team to the West shortened the conference gap by essentially increacing 'n'!
- The more closely the two conferences resemble each other in terms of number of teams and number of districts the more "fair" the playoff system is.

![](Images/GapVis.png)
![](Images/gapvis20172018.png)
